Probe or Wait: Handling tail losses using Multipath TCP

### 2017-04-27 main.tex
minor text fixes in III.

%\kern-1em
\subsection{Testing retransmission mechanism with deterministic loss patterns}
In order to understand the retransmission behavior of the Linux MPTCP implementation and to reproduce the observed retransmissions, we use a 
deterministic drop pattern. Losses are generated by associating netem with corresponding interfaces and dropping select packets. This process 
is simplified by using the KAUNetem tool~\cite{Garcia2016}, which allows an experimenter to e.g., drop packets based on their positions in a flow. 
A MPTCP connection starts with a single TCP subflow and subsequently, one or more subflows are added following an agreement between the client 
and the server. So one has to wait both in time and packets for the second subflow establishment. We send two bursts of 80 packets each and drop 
packets at the tail of the second burst at one of the interfaces. This is to ensure that the necessary and sufficient conditions for probe triggering 
are met and a tail loss probe is generated on that subflow. We calculate the burst completion time for the second burst that has specified tail 
losses. The objective of this experiment is to evaluate retransmission mechanisms with tail loss (single packet loss and multiple tail loss) and 
temporary path loss. Three test cases are considered for the experiments: single packet tail loss and two packet tail loss for tail loss evaluation 
and single packet along with probe~(in TLP) or retransmission~(in RTO) loss for path loss evaluation.

>>>>

%\kern-1em
\subsection{Testing retransmission mechanisms with deterministic loss patterns}
In order to understand the retransmission behavior of the Linux MPTCP implementation and to reproduce the observed retransmissions, we use a 
deterministic drop pattern. Losses are generated by associating netem with corresponding interfaces and dropping select packets. This process 
is simplified by using the KAUNetem tool~\cite{Garcia2016}, which allows an experimenter to e.g., drop packets based on their positions in a flow. 
A MPTCP connection starts with a single TCP subflow and subsequently, one or more subflows are added following an agreement between the client 
and the server. So one has to wait both in time and packets for the second subflow establishment. We send two bursts of 80 packets each and drop 
packets at the tail of the second burst at one of the interfaces. This is to ensure that the necessary and sufficient conditions for probe triggering 
are met and a tail loss probe is generated on that subflow. We calculate the burst completion time for the second burst that has specified tail 
losses. The objective of this experiment is to evaluate retransmission mechanisms with tail loss (single packet loss and multiple tail loss) and 
temporary path loss. Three test cases are considered for the experiments: single packet tail loss and two packet tail loss for tail loss evaluation 
and single packet along with probe~(in TLP) or retransmission~(in RTO) loss for path loss evaluation.
